---
title: "The Miles per Gallon Predictifier"
author: "Jeremy Dean"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(caret)
library(randomForest)
```


## Use & Target Market

A cars' fuel efficiency is very important to the environment and consumers alike. This app is used to predict the miles per gallon of a car gets using ten predictors. This allows auto manufacturers to get an estimate on a new car's fuel economy before going into production.

## The App
Takes eleven inputs from the user starting with selecting the prediction model. It uses data from the mtcars data set.
The predictors:

- 7 slider inputs : displacement, horsepower, rear axle ratio, weight, quarter mile time, and carburetors.
- 4 drop-down menus: model, cylinders, transmission type, and engine shape.
- One numerical input for gears.

The last two slides will contain code and summaries of the two prediction models.

## The Models: Linear Regression
```{r lm}
linFit <- lm(mpg ~ . , data = mtcars)
summary(linFit)$coefficients
```

## The Models: Random Forest
```{r rf}
rfFit <- train(mpg ~ . , data = mtcars, method = "rf")
rfFit
```